TODO: A Survey of StarCraft AI Techniques

### 2012-05-30 survey.tex
small addition

\paragraph*{Protoss Beast Jelly (Protoss)}

>>>>

\paragraph*{Protoss Beast Jelly (Protoss)}
always goes for a 5-gate Zealot rush, supported by an effective harvesting 
strategy named power-mining (2 probes are assigned to every mineral patch,
thereby needing 18 probes for 100\% saturation in a normal map, prior
to expanding). Gas is not mined as it is not needed for constructing Zealots.
